Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-30 W13report.tex
Spell checking.

\begin{table}
\centering
\begin{tabular}{clcccc}
\hline
\multicolumn{5}{|c|}{Per Sensor MSE Comparison} \\
\hline
Visit    & Prefilter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
\hline
v6866601 & True      & 0      & 2        & 22 & 4\\
         & False     & 4      & 6        & 24 & 10\\
v6866602 & True      & 3      & 5        & 7 & 2\\
         & False     & 6      & 7        & 8 & 6\\
v6866603 & True      & 6      & 7        & 3 & 1\\
         & False     & 6      & 8        & 3 & 1\\
\end{tabular}
\caption{
We exampine the configs chosen based on the minimum MSE and compare them to the config of the
minimum number of false positives.  The sample here consists of 9 sensors per visit.  
N$_{Same}$ is the number of times the minimum MSE coincides with the minimum false positives.  N$_{<3}$
is the number of times the minimum false positive config has an MSE in the minimum 3.  $\Delta FP$
is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
false positives per sensor.  max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
\label{tab-MSE_persensor}}
\end{table}

@@

\begin{figure}%
\captionsetup[subfloat]{labelformat=empty}
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
\caption{Here we show the comparison of detected false positive count to the analytic predition.
In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  
The top row has had the counts corrected for the underestimate of the noise by the variance plane.  This is a 
1\% correction in the case of prefiltering and a 4\% correction to the variance in the postfiltering case.
In the bottom row we have corrected the predicted counts to coincide with the measured values.  From left to right
this is a 5\%, 3\%, 2\% correction to the variance respectively.  The shaded area is the 1-$\sigma$ confidence envelope
determined from Monte Carlo simulations assuming the analytic form of the false positive rate and a Gaussian distribution.}
\label{fig-fp_v_thresh}
\end{figure}

>>>>

\begin{table}
\centering
\begin{tabular}{clcccc}
\hline
\multicolumn{5}{|c|}{Per Sensor MSE Comparison} \\
\hline
Visit    & Prefilter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
\hline
v6866601 & True      & 0      & 2        & 22 & 4\\
         & False     & 4      & 6        & 24 & 10\\
v6866602 & True      & 3      & 5        & 7 & 2\\
         & False     & 6      & 7        & 8 & 6\\
v6866603 & True      & 6      & 7        & 3 & 1\\
         & False     & 6      & 8        & 3 & 1\\
\end{tabular}
\caption{
We examine the configs chosen based on the minimum MSE and compare them to the config of the
minimum number of false positives.  The sample here consists of 9 sensors per visit.  
N$_{Same}$ is the number of times the minimum MSE coincides with the minimum false positives.  N$_{<3}$
is the number of times the minimum false positive config has an MSE in the minimum 3.  $\Delta FP$
is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
false positives per sensor.  max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
\label{tab-MSE_persensor}}
\end{table}

@@

\begin{figure}%
\captionsetup[subfloat]{labelformat=empty}
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
\caption{Here we show the comparison of detected false positive count to the analytic prediction.
In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  
The top row has had the counts corrected for the underestimate of the noise by the variance plane.  This is a 
1\% correction in the case of prefiltering and a 4\% correction to the variance in the postfiltering case.
In the bottom row we have corrected the predicted counts to coincide with the measured values.  From left to right
this is a 5\%, 3\%, 2\% correction to the variance respectively.  The shaded area is the 1-$\sigma$ confidence envelope
determined from Monte Carlo simulations assuming the analytic form of the false positive rate and a Gaussian distribution.}
\label{fig-fp_v_thresh}
\end{figure}
